### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0f  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &1&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&10.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0f& 4096 & 12.0 &12&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 1060.8 min & 24.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}. First, as the result indicates, the leakage sites that leak more information (> 5.0 bits) are all fixed in OpenSSL 1.1.1. The result indicates that \ctool{} can help developers identify side-channel leakages and pick the severe from them automatically. As expected, we find most of the leakages are from the big number calculations. OpenSSL has a side-channel mitigated big number implementation. As long as big numbers are derived from secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}. However, the flag is off by default. We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}. Second, for those leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information. For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd. However, it is not a side-channel leakage vulnerability. Both tools report the leakage site can leak one bit of information. Third, even \tool{} reports some leakage sites leak little information, \ctool{} can report the vulnerability is severe. \tool{} quantifies the amount of leaked information for one execution. So it is possible that some leakage sites leak little information for one input but leak more information for a different input.

@@

%% TODO
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as a service. The machine learning service provider uploads the trained model into an enclave running on the cloud platform and provides a machine learning service to a third-party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.

>>>>

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0f  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &1&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &7&6&10.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0f& 4096 & 12.0 &12&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 1060.8 min & 24.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}. First, as the result indicates, the leakage sites that leak more information (> 5.0 bits) are all fixed in OpenSSL 1.1.1. The result indicates that \ctool{} can help developers identify side-channel leakages and pick the severe from them automatically. As expected, we find most of the leakages are from the big number calculations. OpenSSL has a side-channel mitigated big number implementation. As long as big numbers are derived from secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}. However, the flag is off by default. We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}. Second, for those leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information. For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd. However, it is not a side-channel leakage vulnerability. Both tools report the leakage site can leak one bit of information. Third, even \tool{} reports some leakage sites leak little information, \ctool{} can report the vulnerability is severe. \tool{} quantifies the amount of leaked information for one execution. So it is possible that some leakage sites leak little information for one input but leak more information for a different input. We run the chi-squared test to determine if any two leaked functions have independent leakages.

@@

%% TODO Analyze the result of the GTK
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as a service. The machine learning service provider uploads the trained model into an enclave running on the cloud platform and provides a machine learning service to a third-party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.
